\subsubsection{What technical information did you learn?}
Working on this project introduced me more to the concept of 3D printing and the functions of a 3D printer and its parts, as well as the different technologies involved.
I also learned how to research and design a technical project, as well as how to write documentation for one.
\subsubsection{What non-technical information did you learn?}
The non-technical information that I learned was how to adapt a pitch to the possible different technical levels of your audience.
From the in-class exercise to presenting at Expo, being able to analyze your audience and present accordingly is a valuable life skill.
\subsubsection{What have you learned about project work?}
From working on this project I learned that it is good to have lots of documentation so that you know exactly what goals you are trying to accomplish and how.
It is also good to have defined roles for each member.
Throughout the development of the project, these are subject to change, but having a good plan will limit the amount of avoidable issues that often come with working on a project.
\subsubsection{What have you learned about project management?}
Project management requires good prioritizing and planning skills, as well as flexibility.
Throughout the course of this project, what helped was setting goals and having a plan of when to accomplish them by.
Of course, due to unforeseen challenges our timeline varied and we had to remain flexible regarding when we wanted to have certain tasks completed by.
\subsubsection{What have you learned about working in teams?}
Working in teams requires a balance of control and dependency. 
While there are tasks that each member may be best-suited for, a successful team needs a lot of productive communication and a good sense of direction and control.
As a part of Group 63, I found that all were self-sufficient, well-working individuals.
The challenge that comes with that is the lack of communication because each person is able to complete tasks well on his or her own.
And while I do not think this caused a problem for us, for future larger projects it could lead to inconsistencies.
\subsubsection{If you could do it all over, what would you do differently?}
If I could do this project all over again, I would take more initiative during the development phases so that I could be more hands-on and involved, specifically with trouble-shooting the hardware.
I felt that the problems with hardware is what restricted our timeline for the most part, and while we did get to where we needed to be by the deadline, I just wish I had been able to help get past sticking points quicker.
 