\subsubsection{Fall Term}
\paragraph{Week 01}
\begin{itemize}
\item Plans: View and submit bids for Capstone project. 
\item Problems: Need to decide top 5 projects and 2 bottom projects I'd like to work on.
\item Progress: Submitted my preferences Thursday. 
\item Summary: Read project proposals and submitted my preferences. 
\end{itemize}
\paragraph{Week 02}
\begin{itemize}
\item Plans: Get group and project assignment.
\item Problems: Need to contact client and begin problem statement draft for project. 
\item Progress: Got in contact with client, started Problem statement draft.
\item Summary: Met group and got project/client assignment, mailed contact, met client for the first time, and began problem statement draft. 
\end{itemize}
\paragraph{Week 03}
\begin{itemize}
\item Plans: Finish and submit individual problem statement. 
First TA meeting. 
Meet with client to get lab access so we can begin getting familiar with 3D printer. 
Get github repo up and put problem statement on it.
\item Problems: Need to get familiar with the established workflow for 3D printing single-color objects.
Need to set up github repo and begin putting all documentation inside.
\item Progress: Completed draft of Problem Statement and submitted PDF to teach. 
Met with client and learned about current workflow, software being used, 3D printed objects.
\item Summary: Completed individual assignment, had first TA meeting, met with client and got lab access, and set up Github repo.
\end{itemize}
\paragraph{Week 04}
\begin{itemize}
\item Plans: Consolidate individual problem statements into one group problem statement to be sent to client and approved.
Meet with TA.
\item Problems: Group Problem Statement due.
Need computer access in ALS 2157 lab to use 3D printer.
Need access to group OneNote.
\item Progress: Completed Group Problem Statement and emailed it to client for approval.
Client responded  with some revisions; made the revisions and resent for approval.
Met with TA.
Client approved our document.
Emailed Kirsten for access to group OneNote.
\item Summary: Completed and sent Group Problem Statement to client, got client approval, we now have computer and lab access and can begin working with the 3D printer.
\end{itemize}
\paragraph{Week 05}
\begin{itemize}
\item Plans: Begin work on Project Requirements document (rough draft due this Friday on OneNote).
\item Problems:  Need to define project requirements, aka what criteria our project be graded on.
\item Progress: Met with group to begin working on document.
\item Summary:  Had TA meeting, began drafting problem requirements document.
\end{itemize}
\paragraph{Week 06}
\begin{itemize}
\item Plans: Project Requirements document.
\item Problems: Need to establish project requirements and send to client for approval.
\item Progress: Completed all our goals for the week.
\item Summary: Finished project Requirements Document and sent to client. 
Client responded with some corrections. 
Made necessary corrections and resubmitted to client.
\end{itemize}
\paragraph{Week 07}
\begin{itemize}
\item Plans: Begin work on tech review.
\item Problems: Need to define 9 different technologies for our project.
\item Progress: Met in the lab to go over established 3D printing workflow and discuss project roles.
\item Summary: Divided up 9 technologies, 3 per person, to begin work on individual tech reviews. 
Rough draft due in class on Tuesday, 11/14.
\end{itemize}
\paragraph{Week 08}
\begin{itemize}
\item Plans: Complete rough draft of individual tech review and bring to class for peer review, TA meeting.
\item Problems: Need to define 3 options for the three pieces of technology assigned to me (filament type, file type, slicing software) and determine which option is best for the project.
\item Progress: Began research on three pieces of technology and possible options.
\item For my portion of the tech review, the pieces and options will be as follows:
	\begin{itemize}
    \item Filament type: PLA, ABS, or Nylon
	\item File type: STL, OBJ, or 3MF
	\item Slicing software: Voxelizer, Simplify3D, or Cura
    \end{itemize}
\end{itemize}
\paragraph{Week 09}
\begin{itemize}
\item Plans: No class Tuesday, finalize draft of tech review.
\item Problems: Need to edit and finish my individual tech review and send digital PDF to Kirsten by 11:59 PM Tuesday.
\item Progress: Finished research and document and submitted. 
\item Summary: Finished and submitted individual technology review. 
Next, design document.
\end{itemize}
\paragraph{Week 10}
\begin{itemize}
\item Plans: Complete and submit Design Doc Friday, 11:59PM.
\item Problems: Need to be able to prioritize time and complete all tasks for all classes.
\item Progress: Worked on design doc both with team and individually. 
Was able to divide up tasks to make the assignment more manageable for us individually.
\item Summary: Completed and submitted design doc by due date, survived dead week.
\end{itemize}
\subsubsection{Winter Term}
\paragraph{Week 01}
\begin{itemize}
\item Plans: Begin the term.
\item Problems: 8AM meeting time T and R, however, only meeting a few times throughout the term.
\item Progress: Not much accomplished this week; first week back. Adjusting to the new term.
\item Summary: Began Winter term. 
Not much happened in terms of project work this week. 
Will be meeting with the group next week as well as have the first TA meeting of the term.
\end{itemize}
\paragraph{Week 02}
\begin{itemize}
\item Plans: Get in contact with client to get Palette+ and feedback/verification on documents. 
Jackson to start python pipeline portion of the project.
\item Problems: No client response since beginning of Christmas break.
\item Progress: Client responded on Tuesday about getting the Palette+ to the group as well as looking at the design document.
\item Summary: We are limited on the progress we can make until we get the Palette+ installed in the lab. 
We have client correspondence and will follow up to get the Palette+ and Design Doc verification. 
Beginning next TA meeting, the TA would like to see some physical representation of project progress every TA meeting.
\end{itemize}
\paragraph{Week 03}
\begin{itemize}
\item Plans:  TA meeting, begin task of looking into how to convert/utilize 3MF files.
\item Problems: Still unable to really begin working with the hardware and interfacing the software with the hardware due to issues getting the Palette+ and Zmorph to produce a successful print.
\item Progress: Began research Thursday.
\item Summary: Will need to keep looking into how we will be using 3mf file type. 
Hopefully the issue with the hardware will be resolved soon.
\end{itemize}
\paragraph{Week 04}
\begin{itemize}
\item Plans:  Meet with group and play catch up after being sick.
\item Problems: I was sick.
Still having hardware (adhesion between the bed and the filament).
\item Progress: Group meeting to go over developments, progress with the hardware, tasks.
\item Summary: Still limited on what we are able to do because of hardware issues. 
\end{itemize}
\paragraph{Week 05}
\begin{itemize}
\item Plans: TA meeting, not much else for this week. 
Begin poster and progress report.
\item Problems: Still having adhesion issues with 3D printer. 
\item Progress: Met with TA, looked at assignment requirements.
\item Summary: Feeling a little at a standstill since we are still having hardware issues. 
But we're getting closer. 
Will need a UML diagram I should look into that.
\end{itemize}
\paragraph{Week 06}
\begin{itemize}
\item Plans:  Submit preliminary poster and midterm progress report.
\item Problems: N/A
\item Progress: Finished poster and emailed to TA. 
Submitted progress report.
\item Summary: Submitted assignments. 
Will need to have a deliverable by week 8 TA meeting.
\end{itemize}
\paragraph{Week 07}
\begin{itemize}
\item Plans: Update design and requirements doc, work on alpha build for next TA meeting.
\item Problems: N/A
\item Progress: Updated docs on Friday.
\item Summary: Getting close to having all requirements done. 
We need to make sure to have a deliverable by next TA meeting.
\end{itemize}
\paragraph{Week 08}
\begin{itemize}
\item Plans: TA Meeting.
\item Problems: N/A
\item Progress: Presented TA with alpha demo, approx. 7/9 requirements met.
\item Summary: Need to update the design and requirements documents, which will bring us closer to having fulfilled all our requirements.
\end{itemize}
\paragraph{Week 09}
\begin{itemize}
\item Plans: TA meeting.
\item Problems: N/A 
\item Progress: Met with TA and scheduled next meeting to be in the lab to demo.
\item Summary: Need to get set up for our beta demo next TA meeting. 
Sent TA updated design and requirements docs.
\end{itemize}
\paragraph{Week 10}
\begin{itemize}
\item Plans: Demo for the TA in the lab in place of TA meeting.
\item Problems: TA did not make it to meeting.
\item Progress: Have implemented all requirements, now just need to debug.
\item Summary: Unable to do lab demo for the TA but all project requirements have been met. 
Will send a video demo instead.
Winter progress report due next Wednesday.
\end{itemize}
\subsubsection{Spring Term}
\paragraph{Week 01}
\begin{itemize}
\item Plans: Schedule TA meeting.
Register for expo.
\item Problems: N/A
\item Progress: Registered for Expo on Wednesday, April 4.
\item Summary: Submitted timeslot for TA meeting time on Friday from 3-5. 
Registered for Expo.
\end{itemize}
\paragraph{Week 02}
\begin{itemize}
\item Plans: TA Meeting on Friday.
Not much left to do besides expo poster and release forms (May 1st).
\item Progress: Had TA meeting and discussed limitations of hardware and future expectations.
\item Problems: N/A
\item Summary: Hardware still limiting us on ability to consistently produce successful prints. 
Need to finalize poster and submit, and turn in release forms.
\end{itemize}
\paragraph{Week 03}
\begin{itemize}
\item Plans: TA Meeting on Friday.
\item Progress: N/A
\item Problems: N/A
\item Summary: Hardware still being serviced, still being a problem. 
TA wants one successful print and then we will be done.
\end{itemize}
\paragraph{Week 04}
\begin{itemize}
\item Plans: TA Meeting on Friday.
Finalize poster and submit through canvas assignment, and submit for printing. 
Turn in release forms.
\item Progress: Completed all tasks listed in the plan.
\item Problems: N/A
\item Summary: Submitted final draft of poster through canvas on Friday. 
Emailed signed release forms on Friday.
TA meeting: Have code ready by Friday, May 11th. 
Do not need checkoff as we had that at the end of last term. 
Further TA meetings will be optional; email for appointment.
\end{itemize}
\paragraph{Week 05}
\begin{itemize}
\item Plans: Work on Spring term Progress Report and Presentation due Sunday, May 6th.
\item Progress: Began working on report and presentation.
\item Problems: N/A
\item Summary: Submitted progress report by the deadline. 
No TA meeting this week.
\end{itemize}
\paragraph{Week 06}
\begin{itemize}
\item Plans: Class on Wednesday.
\item Progress: Attended class.
\item Problems: N/A
\item Summary: Had class on Wednesday and were given reminders for Expo (next Friday).
\end{itemize}
\paragraph{Week 07}
\begin{itemize}
\item Plans: Expo on Friday!
\item Progress: Prepared for Expo.
\item Problems: N/A
\item Summary: Presented our project at Expo.
\end{itemize}
\paragraph{Week 08}
\begin{itemize}
\item Plans: Go to class Wednesday.
\item Progress: Attended class.
\item Problems: N/A
\item Summary: Class on Wednesday, reminded to do final project handoff and about various upcoming assignments.
\end{itemize}
\paragraph{Week 09}
\begin{itemize}
\item Plans: Contact client to schedule final handoff (in form of a demo).
Upcoming assignments: Peer review, final presentation (Due Friday, June 8), final report (Due Tuesday, finals week).
\item Progress: Emailed client to request meeting on Wednesday, May 30th.
\item Problems: No client response by the end of the week.
\item Summary: Emailed client. 
No response yet by the end of the week, will email again if nothing heard over the weekend. 
Completed peer review this week.
\end{itemize}
\paragraph{Week 10}
\begin{itemize}
\item Plans: Email client again to request demo.
Begin work on final presentation (due Friday) and final report (due next Tuesday).
Class Wednesday.
\item Progress: Client responded Thursday with his availability. 
Scheduled demo for Friday at 2:30PM.
Attended class Wednesday, which consisted of students giving feedback regarding their time here at OSU.
\item Problems: N/A
\item Summary: Presented final project to client in the form of an in-lab demo during which the software and hardware components were presented.
Began, completed, and submitted our final presentation.
Last assignment, final report, due Tuesday.
\end{itemize}