\subsubsection{What technical information did you learn?}
Through the course of this project, I gained technical insights in both the hardware and software aspects of development. In terms of hardware, I obtained a relatively solid background in the process of 3D printing, starting with a structural file to production of the print. I learned the nomenclature associated with the hardware devices, and the intended functionality of particular components, like the extruder or multi-filament interface. In terms of software, I learned new concepts like operating system interoperability and execution of dependent software tools that were not natively accessible from a command-line environment.
\subsubsection{What non-technical information did you learn?}
While the project involved mostly technical subjects, I managed to learn a few skills that can be put to use later in my career. I learned proper communication standards that are to be expected when interacting with a client, and how bargaining might take place in terms of work to be completed on a proposed project. I also gleaned experience in time management and information retrieval for new concepts encountered during development.
\subsubsection{What have you learned about project work?}
In development of the project I discovered the importance of time management. The weekly TA meetings served as a constant reminder that there was work to be completed. At some points I found myself scrambling to meet deadlines which created stress that could have been circumvented through the implementation of better personal scheduling.
\subsubsection{What have you learned about project management?}
I found that documentation plays a massive roll in the management of a project. There were a couple of instances during the three terms where I felt I could have taken more in-depth notes or better recorded completed work for future reference. Including such notes allow for a reduction in the amount of work that must initially be completed when returning to development after a break between terms or in switching from other work from courses being completed concurrently with the capstone series.
\subsubsection{What have you learned about working in teams?}
Our group was efficient, communicated well while also being self-sufficient. Due to the lack of any real problems with the dynamic between members I don't believe there was too much to learn. The weekly TA meetings gave us a way to track each others progress on our respective parts of the project. We maintained a group text message throughout all three terms which provided us a way to quickly get in touch with everyone when issues were encountered. 
\subsubsection{If you could do it all over, what would you do differently?}
If we were to begin the project again from Fall term, I would attempt to bargain more with the client to procure better printing hardware. I believe adhesion and filament issues are what were the most detrimental to development, and that most of these issues could have been avoided if we had access to hardware that was closer to industry standards. With the elimination of these complications we could have considered the outlined stretch goals like the production of a publication or the implementation of a GUI to reduce the need for prior experience in a command-line environment.