\subsubsection{Fall Term}
\paragraph{Week 01}
\begin{itemize}
\item Selected preferences from project list
\item Submitted resume and personal biography.
\end{itemize}
\paragraph{Week 02}
\begin{itemize}
\item Met with client.
\item Met with group.
\item Having some issues with the scheduling of our weekly TA meeting, all group members are available at different times and I have class during every time provided by the TA. I emailed the TA in hopes of working through the issue, which we currently are. 
\end{itemize}
\paragraph{Week 03}
\begin{itemize}
\item Worked individually on the problem statement.
\item Met with the client again, this time in the lab where the 3D printers are housed. 
\item We established a GitHub page and invited the client and another individual 
In the department that has a stake in the project.
\end{itemize}
\paragraph{Week 04}
\begin{itemize}
\item Met with TA
\item Consolidated problem statement.
\item The client had 3-4 minor suggestions for edits, which were corrected and submitted.
\end{itemize}
\paragraph{Week 05}
\begin{itemize}
\item Requirements document partly drafted.
\item Some prints completed using the printer.
\item Set future times to continue work on the requirements document.
\end{itemize}
\paragraph{Week 06}
\begin{itemize}
\item Requirements document finalized.
\item Gantt chart created for addition to the requirements document.
\item The client approved our document, with a few grammatical corrections.
\end{itemize}
\paragraph{Week 07}
\begin{itemize}
\item Technology Review partially written.
\item Our group met to get hands on time with the printer, and to get a set list of technological components that are included in our project. We divided up the components equally and proceeded from there.
\end{itemize}
\paragraph{Week 08}
\begin{itemize}
\item Gained insight from peer review of technology review.
\item Continued work on the technology review.
\end{itemize}
\paragraph{Week 09}
\begin{itemize}
\item Finalized and submitted the technology review.
\end{itemize}
\paragraph{Week 10}
\begin{itemize}
\item Began and finalized the design document with the group.
\end{itemize}

\subsubsection{Winter Term}
\paragraph{Week 01}
\begin{itemize}
\item Communication was reestablished with the TA and a meeting was set for the following week.
\end{itemize}
\paragraph{Week 02}
\begin{itemize}
\item Met with the TA to provide feedback on the previous term and overview the current term.
\item I was given the goal of implementing the input handling functions by next week's meeting.
\end{itemize}
\paragraph{Week 03}
\begin{itemize}
\item Input handling was implemented.
\item Skeleton code was produced to outline the remaining aspects of the work-flow's software.
\end{itemize}
\paragraph{Week 04}
\begin{itemize}
\item Met with the group and the TA on separate occasions. Group meeting served to summarize the TA meeting due to sickness related absences.
\item A new goal of investigating the process for handling of PDB files was set for completion by the next TA meeting.
\item The hardware aspect of the work-flow was presenting numerous issues, preventing print production.
\end{itemize}
\paragraph{Week 05}
\begin{itemize}
\item I was able to replicate the O and H STL files provided by the client! This is a big step forward in terms of project development. We should now in theory be able to produce polychromatic prints of biological molecules.
\item The software tools to be utilized in the work-flow were locked in, and are now ready for implementation.
\item Results were shared at the TA meeting. Conveniently timed, we have also been able to produce a polychromatic test print using the new hardware.
\end{itemize}
\paragraph{Week 06}
\begin{itemize}
\item System commands were investigated and implemented (for Chimera and Cura) to execute the dependent printing software tools from the work-flow script.
\item The next task of input file validation was assigned.
\end{itemize}
\paragraph{Week 07}
\begin{itemize}
\item Met with the TA.
\item Development/investigation of file validation continued.
\end{itemize}
\paragraph{Week 08}
\begin{itemize}
\item Added Chroma to the pipeline (system calls) and finalized file validation in time for the alpha deliverable.
\item Met with Daniel on Tuesday to show our alpha deliverable. We went over the requirements and design documents and discussed revisions. 
\end{itemize}
\paragraph{Week 09}
\begin{itemize}
\item Met with the TA and set a time to exhibit the beta demo of the work-flow.
\item Implemented further revisions to the design and requirements documents
\end{itemize}
\paragraph{Week 10}
\begin{itemize}
\item A miscommunication occurred between the group and the TA and the meeting was not conducted. The TA believed we would first meet in Kelley and then walk to the lab. The group met in the lab.
\item The TA requested a video be recorded to exhibit beta performance and one was supplied.
\end{itemize}

\subsubsection{Spring Term}
\paragraph{Week 01}
\begin{itemize}
\item A Friday meeting time was established with the group and TA.
\item Having provided a beta demo last term a week 1 meet was deemed unnecessary.
\end{itemize}
\paragraph{Week 02}
\begin{itemize}
\item Met with the TA.The meeting was brief and the group had a discussion following the TA meeting to get some things sorted out with upcoming assignments.
\item We plan to begin revisions on the poster this weekend and into next week.
\end{itemize}
\paragraph{Week 03}
\begin{itemize}
\item Met with the TA. General check in on progress.
\end{itemize}
\paragraph{Week 04}
\begin{itemize}
\item Met with the TA. General check in on progress.
\end{itemize}
\paragraph{Week 05}
\begin{itemize}
\item Began and finalized work on the midterm progress report.
\end{itemize}
\paragraph{Week 06}
\begin{itemize}
\item Added support for Windows and OSX operating systems too the software work-flow.
\item Finalized file validation and added comments throughout the code.
\item Successfully produced a polychromatic print of a molecule.
\end{itemize}
\paragraph{Week 07}
\begin{itemize}
\item Presented our project at Expo
\end{itemize}
\paragraph{Week 08}
\begin{itemize}
\item Cool down week.
\end{itemize}
\paragraph{Week 09}
\begin{itemize}
\item Contacted the client in regards to the project hand off, no response.
\end{itemize}
\paragraph{Week 10}
\begin{itemize}
\item Conducted the product hand off with the client. Provided overviews of the hardware and software aspects of the project.
\item Met with the TA. Discussed the hand off and remaining work to be completed before the term ended.
\end{itemize}