\subsubsection{What technical information did you learn?}
For my portion of the project which was primarily focused on the hardware; thus, the majority of the technical information that I learned was centered around the hardware. I gained a much greater understanding of the intricacies of 3D printing hardware and some of the software tools that interface with said hardware. This included things such as common issues with 3D printers and the relatively early state of multifilament printing at the consumer level.
\subsubsection{What non-technical information did you learn?}
Relative to the amount of technical information that I learned working on this project, I do not think I learned much new non-technical information. For me the structure of the course and nature of our project was not overly conducive to introducing new non-technical information. The one exception to this was preparing and participating in the expo. I had not previously participated in an event of that scale and it was interesting to experience it with my group members.
\subsubsection{What have you learned about project work?}
One point that was reinforced over the course of the project was to ensure that communication with the client was kept open during crucial times during the project such as the initial documentation and the final hand-off of the deliverables at the end of this term.
\subsubsection{What have you learned about project management?}
I learned that it is important to have clearly defined goals at the start of the project and an action plan in place to accomplish those goals.
\subsubsection{What have you learned about working in teams?}
The most important point that was reinforce over the course of the project was maintaining consistent communication with my teammates to ensure that problems are addressed in a timely manner and that collaborative efforts can be made more effective.
\subsubsection{If you could do it all over, what would you do differently?}
If I could do one thing differently it would be to spend more time testing four colored prints. This was one of the things that I wanted to do but was unable to finish before expo.