\subsubsection{Fall Term}
\paragraph{Week 01}
\begin{itemize}
\item This week I submitted my choices for potential CAPSTONE projects. 
\end{itemize}
\paragraph{Week 02}
\begin{itemize}
\item Had the initial meeting with group members and Dr. Hsu and covered the basics of the projects. 
\end{itemize}
\paragraph{Week 03}
\begin{itemize}
\item Worked on and submitted the rough draft of the problem statement. 
\item Had a second meeting with Victor to tour the lab and the equipment.  
\end{itemize}
\paragraph{Week 04}
\begin{itemize}
\item Met with group for finalize the problem statement and turned in the final draft. 
\item Started messing with the 3d printer. 
\end{itemize}
\paragraph{Week 05}
\begin{itemize}
\item Met with Daniel on Tuesday and worked on and submitted the rough draft of the requirements document. 
\end{itemize}
\paragraph{Week 06}
\begin{itemize}
\item This week we met with Daniel and completed the final draft of the requirements document. 
\end{itemize}
\paragraph{Week 07}
\begin{itemize}
\item The group met in the lab to go over some of the tech review components. 
\end{itemize}
\paragraph{Week 08}
\begin{itemize}
\item Worked on the rough draft of the tech review. 
\end{itemize}
\paragraph{Week 09}
\begin{itemize}
\item Worked on and turned in final draft of tech review. 
\end{itemize}
\paragraph{Week 10}
\begin{itemize}
\item Had the weekly meeting with Daniel.
\item Worked on and submitted the final draft of the design document. 
\end{itemize}

\subsubsection{Winter Term}
\paragraph{Week 01}
\begin{itemize}
\item Had the initial Capstone meeting for winter term on Tuesday. 
\end{itemize}
\paragraph{Week 02}
\begin{itemize}
\item Had the initial meeting with Daniel for the Winter term. 
\item Got a hold of the Palette and removed the filament blockage. 
\end{itemize}
\paragraph{Week 03}
\begin{itemize}
\item Met with Daniel and finished the basic setup of the Palette. 
\end{itemize}
\paragraph{Week 04}
\begin{itemize}
\item Met with Daniel on Tuesday.
\item Continued working on the Palette.
\item Met with group on Friday.
\end{itemize}
\paragraph{Week 05}
\begin{itemize}
\item Met with Daniel. 
\item Successfully got the first multicolored print. 
\item Started printing with the water molecule files that were sent by Victor. 
\item Unable to finish the print due to support issues. However the transition tower did successfully adhere to the print bed. 
\end{itemize}
\paragraph{Week 06}
\begin{itemize}
\item Worked on and submitted the midterm progress report. 
\end{itemize}
\paragraph{Week 07}
\begin{itemize}
\item Continued working on the project and troubleshooting any remaining adhesion issues with the printer. 
\item Met with Daniel on Tuesday.
\end{itemize}
\paragraph{Week 08}
\begin{itemize}
\item Continued working on the project and troubleshooting any remaining adhesion issues with the printer.
\item Met with Daniel on Tuesday.
\end{itemize}
\paragraph{Week 09}
\begin{itemize}
\item Got the adhesion issues mostly solved and successfully printed the first molecule. 
\item Met with Daniel and discussed the demo for the next week. 
\end{itemize}
\paragraph{Week 10}
\begin{itemize}
\item Unable to meet with Daniel due to a miscommunication. 
\item Sent Daniel a video demo of the software as requested.
\end{itemize}

\subsubsection{Spring Term}
\paragraph{Week 01}
\begin{itemize}
\item Continued working on the project. 
\item Setup meeting time with Daniel.
\end{itemize}
\paragraph{Week 02}
\begin{itemize}
\item Had the initial meeting with Daniel for the Spring term. 
\end{itemize}
\paragraph{Week 03}
\begin{itemize}
\item Met with Daniel. 
\item Worked on four color print.
\end{itemize}
\paragraph{Week 04}
\begin{itemize}
\item Met with Daniel. 
\item Worked on four color print.
\end{itemize}
\paragraph{Week 05}
\begin{itemize}
\item No meeting with Daniel this week.
\item Worked on midterm progress report.
\end{itemize}
\paragraph{Week 06}
\begin{itemize}
\item Made successful print for expo.
\item No meeting with Daniel this week.
\end{itemize}
\paragraph{Week 07}
\begin{itemize}
\item Expo
\end{itemize}
\paragraph{Week 08}
\begin{itemize}
\item No TA meeting this week. 
\item Went to the Wednesday class session. 
\end{itemize}
\paragraph{Week 09}
\begin{itemize}
\item No TA meeting this week.
\item Emailed Victor for final hand-off. 
\end{itemize}
\paragraph{Week 10}
\begin{itemize}
\item Met with Victor to hand-off project on Friday.
\item Met with Daniel on Friday for final TA meeting. 
\end{itemize}